Cloud correction and filtering of operational microwave humidity radiances with case specific uncertainty estimation

### 2020-09-21 Article/ici_submm_cloudcorr.tex
started writing sec 3.3.1

\introduction
%
Satellite observations of humidity inside the troposphere are mainly performed
by downward-looking sensors. Among this class of observations, the frequency
range around 183\,GHz has a special position. Water vapour has a noticeable
transition at 22\,GHz, but it is relatively weak and only column values can be
derived \citep[e.g.][]{schluessel1990atmospheric} for the observation geometry
of concern. The first transition in the microwave region that can be used to
derive altitude information, i.e.\ can be used for ``sounding'', is the one at
183.31\,GHz \citep{kakar1983retrieval,wang1983profiling}. On the other hand, at
infrared wavelengths a high number of water vapour transitions are found,
including some of high strength. As a consequence, infrared sounders can
provide humidity profiles with high precision and good vertical resolution, but
with strong limitations imposed by clouds. To be able to also sense humidity
inside and below clouds, weather satellites are since some time equipped with
channels around 183\,GHz. Today such channels are part of several sensors, such
as ATMS (Advanced Technology Microwave Sounder, \citet{weng2012introduction}).

@@

The main motivation for introducing 183\,GHz channels in operational sensors is
numerical weather prediction (NWP). Usage of passive microwave data by
``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
but 183\,GHz data are still mainly used in a clear sky fashion
\citep{geer2018all}. The later is particularly true in NWP of regional scope
\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
weather agencies will likely not be reached in many years. Anyhow, the cloud
filtering applied differs between NWP centres. One approach is to make use of a
``scattering index'' \citep{bennartz2002precipitation}, based on the
observations alone. Today, likely more common is to use ``observation minus
background'' (O-B), where the forecast model is used to obtain an estimate of
the expected clear-sky value and the observation is rejected if the deviation
exceeds some threshold (???). In both cases, the filtering typically involves
observations around 89 and/or 150\,GHz.

Despite the broad usage these filtering methods have some drawbacks. For
183\,GHz, the impact of hydrometeors systematically causes a decrease in the
observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This means that if any cloud
contamination is missed by the filtering this will cause a negative bias in
mean radiance, compared to the true clear-sky mean. This bias will translate to
a bias in humidity after the retrieval or assimilation. The alternative is to
apply a very strict filtering, but this will result in that a high fraction of
actually clear-sky values will be rejected, i.e.\ an important loss of useful
data.

@@

A maybe less obvious problem is the uncertainty to assign to the filtered
values. To our best knowledge, so far only estimates of mean and worst case
errors have been provided. Some cases with relatively high cloud impact will
likely be missed, while most cases are clear sky from start. As the remaining
cloudy cases can cause significant biases, the likely solution is to apply a
quite conservative (high) error estimate. However, this will unnecessary
downgrade the value of the truly clear sky cases and the observations are used
in a non-optimal manner.

@@

The estimation of NFCS values makes use of a special type of machine learning,
denoted as Quantile Regression Neural Network (QRNN,
\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
only some kind of best estimate is provided, QRNN works in a Bayesian fashion
and instead gives a description of the posterior uncertainty. More precisely,
QRNN outputs an user specified set of percentiles that gives a discrete
description posterior distribution, that can be process to derive e.g.\ the
expectation value.

@@

\subsubsection{Uncertainty quantification}
\label{sec:prediction_uncertainty}
%f 
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
	\caption{The prediction uncertainty  for I2V  with respect to quantiles for randomly selected 1500 cases. The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}). The results are from QRNN-single.}
	\label{fig:prediction_uncertainty_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I1V.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-single and QRNN-all for I1V. }
	\label{fig:calibration_I1V}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}

@@

\subsection{MWI}
%
In this section, we present results from QRNN when applied to MWI channels. Firstly, we discuss results when all 183\,GHz MWI channels are used for ``self'' cloud filtering/correction (QRNN-mwi). We also describe the performance of QRNN when sub-mm channels from ICI are used to train MWI channels.
\subsubsection{MWI alone}
%
%t
\begin{table*}[t]
	\caption{Error statistics for predictions from QRNN-mwi. The labels Filtered(5\,K), Predicted(All) and Predicted(5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
	\label{tab:statistics_mwi-alone}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
		\middlehline
		MWI-14 		&bias     & 0.00 & -1.87 & -0.45 & -0.18 & -0.15 \\
					&mae      & 0.64 &  2.31 &  0.91 &  0.96 &  0.80 \\
					&std      & 0.81 &  8.97 &  1.54 &  1.73 &  1.29 \\
					&skewness & 0.03 & -8.32 & -4.02 & -1.09 & -3.06 \\
		\middlehline
		MWI-15 		&Bias     & -0.01 & -1.23 & -0.36 & -0.16 & -0.13 \\
					&MAE      &  0.64 &  1.70 &  0.85 &  0.62 &  0.53 \\
					&STD      &  0.80 &  6.48 &  1.33 &  1.23 &  0.97 \\
					&skewness &  0.01 & -9.96 & -3.32 & -3.06 & -4.17 \\
		\middlehline	
		MWI-16 		&Bias     & -0.00 &  -0.84 & -0.26 & -0.15 & -0.12 \\
					&MAE      &  0.64 &   1.35 &  0.78 &  0.53 &  0.47 \\
					&STD      &  0.80 &   5.31 &  1.15 &  1.03 &  0.80 \\
					&skewness & -0.01 & -12.08 & -3.05 & -5.09 & -4.94 \\	
		\middlehline			
		MWI-17 		&Bias     & -0.00 &  -1.06 & -0.31 & -0.16 & -0.12 \\
					&mae      &  0.64 &   1.54 &  0.80 &  0.62 &  0.54 \\
					&std      &  0.80 &   6.22 &  1.22 &  1.12 &  0.90 \\
					&skewness &  0.01 & -11.06 & -3.31 & -4.35 & -4.33 \\	
		\middlehline			
		MWI-18 		&Bias     & -0.00 &  -0.66 & -0.23 & -0.11 & -0.08 \\
					&mae      &  0.64 &   1.17 &  0.76 &  0.62 &  0.57 \\
					&std      &  0.80 &   4.57 &  1.13 &  1.08 &  0.88 \\
					&skewness &  0.01 & -13.56 & -3.28 & -4.67 & -3.80 \\	
		\bottomhline				
	\end{tabular}	
	\belowtable{} % Table Footnotes
\end{table*}
QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, which lack the higher frequency channels. Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI. For MWI-14, the predictions from QRNN-mwi are only partially successful in removing the cloudy impact. The prediction errors for the complete testing dataset are highly symmetric but with a large spread. The average error bias of measurements from NFCS values is -1.87\,K, and after correction, it reduces to -0.18\,K. The corresponding standard deviation values are 9.01\,K and 1.87\,K. When cases with 5\,K correction are filtered out from the predicted dataset, the bias reduced further to -0.16\,K and MAE from 1.13\,K to 0.97\,K. Though there is a small increase in the accuracy, the high errors indicate residual cloud impact. For MWI-15, a slightly better accuracy than MWI-14 is observed. For this channel, the average error bias in the measurements is -1.23\,K, which  reduces -0.15 after correction.  
\subsubsection{MWI and ICI}
%t
\todo{Incomplete}

\begin{table*}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-single.}
	\label{tab:statistics_mwi}
	\begin{tabular}{llrr|rrr}
		\tophline
				&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
				\cline{3-7}
				%		\hline
				&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
		\middlehline
		MWI-15  &Bias     &  0.00 & -1.23 & -0.26 & -0.04 & -0.03 \\
				&MAE      &  0.64 &  1.70 &  0.76 &  0.56 &  0.50 \\
				&STD      &  0.81 &  6.48 &  1.01 &  0.86 &  0.64 \\
				&Skewness & -0.00 & -9.97 & -1.15 & -1.78 & -0.15 \\
		\middlehline
		MWI-16  &Bias     & 0.00 &  -0.85 & -0.22 & -0.06 & -0.05 \\
				&MAE      & 0.64 &   1.34 &  0.73 &  0.55 &  0.50 \\
				&STD      & 0.80 &   5.31 &  0.96 &  0.83 &  0.63 \\
				&Skewness & 0.01 & -12.08 & -1.02 & -2.25 & -0.11 \\
		\bottomhline			
	\end{tabular}	
	\belowtable{} % Table Footnotes
\end{table*}
In this section, we combine the measurements from MWI-15(MWI-16) and the ICI sub-mm channels to predict MWI-15(MWI-16). Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and thus results for them are not shown separately.

@@

\subsection{AWS}
%
%t
\begin{table*}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels AWS channels. Results are from QRNN-single. }
	\label{tab:statistics_qrnn_aws}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
		\middlehline
		AWS-32  &Bias     & -0.00 & -1.34 & -0.29 & -0.04 & -0.03 \\
		&MAE       &  0.36 &  1.58 &  0.54 &  0.62 &  0.53 \\
		&STD      &  0.45 &  5.91 &  0.92 &  0.98 &  0.73 \\
		&skewness & -0.03 & -7.48 & -3.80 & -1.49 & -1.59 \\
		\middlehline
		AWS-33	&Bias     & -0.01 & -0.98 & -0.25 & 0.02 &  0.01 \\
		&MAE      &  0.36 &  1.23 &  0.51 & 0.49 &  0.42 \\
		&STD      &  0.45 &  4.70 &  0.80 & 0.76 &  0.56 \\
		&skewness & -0.00 & -8.78 & -2.92 & 0.04 & -0.79 \\

>>>>

\introduction
%
Satellite observations of humidity inside the troposphere are mainly performed
by downward-looking sensors. Among this class of observations, the frequency
range around 183\,GHz has a special position. Water vapour has a noticeable
transition at 22\,GHz, but it is relatively weak and only column values can be
derived \citep[e.g.][]{schluessel1990atmospheric} for the observation geometry
of concern. The first transition in the microwave region that can be used to
derive altitude information, i.e.\ can be used for ``sounding'', is the one at
183.31\,GHz \citep{kakar1983retrieval,wang1983profiling}. On the other hand, at
infrared wavelengths a high number of water vapour transitions are found,
including some of high strength. As a consequence, infrared sounders can
provide humidity profiles with high precision and good vertical resolution, but
with strong limitations imposed by clouds. To be able to also sense humidity
inside and below clouds weather satellites are since some time equipped with
channels around 183\,GHz. Today such channels are part of several sensors, such
as ATMS (Advanced Technology Microwave Sounder, \citet{weng2012introduction}).

@@

The main motivation for introducing 183\,GHz channels in operational sensors is
numerical weather prediction (NWP). Usage of microwave data by ``all-sky''
assimilation is growing \citep{geer2017growing}, but 183\,GHz data are still
mainly used in a clear sky fashion \citep{geer2018all}. The later is
particularly true in NWP of regional scope, all-sky assimilation of 183\,GHz at
many national weather agencies will likely not be reached in many years. The
cloud filtering in NWP differs between centres. One approach is to make use of
a ``scattering index'' \citep{bennartz2002precipitation}, based on the
observations alone. Today, likely more common is to use ``observation minus
background'' (O-B), where the forecast model is used to obtain an estimate of
the expected clear-sky value and the observation is rejected if the deviation
exceeds some threshold (???). In both cases, the filtering typically involves
observations around 89 and/or 150\,GHz.

Despite the broad usage these filtering methods have some drawbacks. For
183\,GHz, the impact of hydrometeors systematically causes a decrease in the
observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This means that if any cloud
contamination is missed by the filtering this will cause a negative bias in
mean radiance, compared to the true clear-sky mean. This bias will translate to
a bias in humidity after the retrieval or assimilation. The alternative is to
apply a very strict filtering, but this will result in that a high fraction of
actually clear-sky values will be rejected \todo{(Reka or better reference)},
i.e.\ an important loss of useful data.

@@

A maybe less obvious problem is the uncertainty to assign to the filtered
values. To our best knowledge, in best case estimates of mean and worst case
errors are provided. Some cases with relatively high cloud impact will likely be
missed, while most cases are clear sky from start. As the remaining cloudy
cases can cause significant biases, the likely solution is to apply a quite
conservative (high) error estimate. However, this will unnecessary downgrade
the value of the truly clear sky cases and the observations are used in a
non-optimal manner.

@@

The estimation of NFSC values makes use of a special type of machine learning,
denoted as Quantile Regression Neural Network (QRNN,
\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
only some kind of best estimate is provided, QRNN works in a Bayesian fashion
and instead gives a description of the posterior uncertainty. More precisely,
QRNN outputs an user specified set of percentiles that gives a discrete
description posterior distribution, that can be process to derive e.g.\ the
expectation value.

@@

\subsubsection{Uncertainty quantification}
\label{sec:prediction_uncertainty}
%f 
\begin{figure}[t]
	\includegraphics[width = 70mm]{Figures/prediction_uncertainty_I2V.pdf}	
	\caption{The prediction uncertainty  for QRNN-single(I2V) with respect to quantiles for randomly selected 1500 cases. The quantiles have been plotted at equidistant points. The black line represents a hypothetical Gaussian distribution of $270\pm0.60$\,K, which is of the order of standard deviation for I2V predictions (see Table~\ref{tab:error_statistics_ici}).}
	\label{fig:prediction_uncertainty_I2V}	
\end{figure}
\begin{figure}[t]
	\includegraphics[height = 70mm]{Figures/calibration_QRNN_I1V.pdf}	
	\caption{Calibration of the prediction intervals obtained from QRNN-single and QRNN-all for I1V. }
	\label{fig:calibration_I1V}	
\end{figure}
\begin{figure*}[t]
	\includegraphics[width=\textwidth]{Figures/PDF_uncertainty_bins_QRNN-single.pdf}	
	\caption{Distribution of errors binned according to their uncertainty. Results are from QRNN-single for channels I1V, I2V and I3V.}
	\label{fig:error_distribution_uncertainty_bins}	
\end{figure*}

@@

\subsection{MWI}
%
In this section, we present results from QRNN when applied to MWI channels. Firstly, we discuss results when all 183\,GHz MWI channels are used for ``self'' cloud filtering/correction (QRNN-mwi). We also describe the performance of QRNN when sub-mm channels from ICI are used to train MWI channels.
\subsubsection{MWI alone}
\todo {Incomplete}

%
%t
\begin{table*}[t]
	\caption{Error statistics for predictions from QRNN-mwi. The labels Filtered(7.5\,K), Predicted(All) and Predicted(7.5\,K) are same as described in Table~\ref{tab:error_statistics_ici}}
	\label{tab:statistics_mwi-alone}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(7.5\,K) \\
		\middlehline
		MWI-14 		&bias     & -0.00 & -1.86 & -0.50(4.06\%) & -0.14 & -0.12 \\
					&mae      &  0.96 &  2.58 &  1.25 &  1.12 &  1.00 \\
					&std      &  1.20 &  9.00 &  1.94 &  1.86 &  1.52 \\
					&skewness &  0.01 & -8.20 & -3.03 & -0.88 & -2.15 \\ 
		\middlehline
		MWI-15 		&bias     & 0.01 & -1.23 & -0.40(2.84\%) & -0.13 & -0.11 \\
					&mae      & 0.95 &  1.99 &  1.18 &  0.74 &  0.66 \\
					&std      & 1.20 &  6.55 &  1.73 &  1.32 &  1.11 \\
					&skewness & 0.01 & -9.67 & -2.34 & -2.44 & -2.89 \\
		\middlehline	
		MWI-16 		&bias     & 0.00 &  -0.85 & -0.29(1.94\%) & -0.12 & -0.10 \\
					&mae      & 0.96 &   1.64 &  1.10 &  0.68 &  0.63 \\
					&std      & 1.20 &   5.39 &  1.54 &  1.15 &  0.96 \\
					&skewness & 0.00 & -11.62 & -1.97 & -3.71 & -3.22 \\	
		\middlehline			
		MWI-17 		&bias     & -0.00 &  -1.04 & -0.32(2.41\%) & -0.13 & -0.11 \\
					&mae      &  0.96 &   1.83 &  1.12 &  0.73 &  0.67 \\
					&std      &  1.20 &   6.29 &  1.59 &  1.21 &  1.02 \\
					&skewness & -0.01 & -10.69 & -2.13 & -3.45 & -3.23 \\	
		\middlehline			
		MWI-18 		&bias     &  0.01 &  -0.66 & -0.26(1.37\%) & -0.12 & -0.10 \\
					&mae      &  0.96 &   1.47 &  1.08 &  0.80 &  0.76 \\
					&std      &  1.20 &   4.66 &  1.51 &  1.23 &  1.08 \\
					&skewness & -0.00 & -12.80 & -2.03 & -2.99 & -2.25 \\	
		\bottomhline				
	\end{tabular}	
	\belowtable{} % Table Footnotes
\end{table*}
QRNN-mwi is designed to provide basis for a cloud correction approach applicable to current satellites, which lack the higher frequency channels. Table~\ref{tab:statistics_mwi-alone} shows the results for all 183\,GHz channels of MWI.

MWI channels have a higher measurement uncertainty than ICI, so a higher filtering threshold is selected. All cases with cloud correction greater than 7.5\,K are considered as cloudy and filtered out. With pure-filtering, only 4\% of the cases are filtered out for MWI-14, but the bias reduces from -1.86\,K to -0.50\,K. For the predictions, the average bias is -0.14\,K. For both filtering and correction, a significant reduction in the errors is observed but the resulting values are still high and indicate only partial success of the method. For other channels also, a similar performance is observed.  For MWI-15, cloud correction reduces the average erros from -1.23\,K to -0.13\,K  and the corresponding decrease in standard deviation is 6.55\,K to 1.32\,K. Filtering the predicted cases improves the bias and standard deviation further by 15\%. Interestingly, even with partial correction, the standard deviation is lower than the measurement noise. For MWI-16, the bias for predictions is -0.12\,K compared to -0.85\,K for the measurements. The corresponding standard deviation is  1.15\, which is again smaller than the measurement noise(1.20\,K). MWI-17 also has a similar performance. MWI-18 is least affected by cloud impact among the five channels. The average deviation of the measurement data to NFCS values is only -0.66\,K which reduces to -0.12\,K with QRNN. After filtering 1.37\% cases with high cloud impact, only a slight improvement in the accuracy is observed but the variability of errors decreases from 1.23\,K to 1.08\,K.

The results from QRNN-mwi show that using 183\,GHz channels for self correction is only partially successful in removing the cloudy cases. Though most of the cases with high cloud impact can be removed, the high errors are mostly due to partially corrected and uncorrected cases with low cloud impact. Using a low threshold filter on the predicted data can improve the accuracy, but at the cost of excessive removal of clear-sky cases. The five channels are sensitive to different regions of the troposhere. The brightness temperature of same cloud measured at different frequencies can vary. This can be quite valuable information to train QRNN. However cloud impact from regions where the weighting functions match poorly cannot be represented adequately in QRNN. The partial correction is a consequence of cases which for which QRNN cannot train.

In contrast to this, the noise reduction for the clear-sky cases is quite significant. The accurate prediction of NFCS values for noisy clear-sky values dominate sthe

\subsubsection{MWI and ICI}
%t
\todo{Incomplete}

\begin{table*}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels MWI-15 and MWI-16. Results are from QRNN-single.}
	\label{tab:statistics_mwi}
	\begin{tabular}{llrr|rrr}
		\tophline
				&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
				\cline{3-7}
				%		\hline
				&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
		\middlehline
		MWI-15  &Bias     &  0.00 & -1.23 & -0.26 & -0.04 & -0.03 \\
				&MAE      &  0.64 &  1.70 &  0.76 &  0.56 &  0.50 \\
				&STD      &  0.81 &  6.48 &  1.01 &  0.86 &  0.64 \\
				&Skewness & -0.00 & -9.97 & -1.15 & -1.78 & -0.15 \\
		\middlehline
		MWI-16  &Bias     & 0.00 &  -0.85 & -0.22 & -0.06 & -0.05 \\
				&MAE      & 0.64 &   1.34 &  0.73 &  0.55 &  0.50 \\
				&STD      & 0.80 &   5.31 &  0.96 &  0.83 &  0.63 \\
				&Skewness & 0.01 & -12.08 & -1.02 & -2.25 & -0.11 \\
		\bottomhline			
	\end{tabular}	
	\belowtable{} % Table Footnotes
\end{table*}
In this section, we combine the measurements from MWI-15(MWI-16) and the ICI sub-mm channels to predict MWI-15(MWI-16). Since we assume that all channels are remapped to a common footprint, channels MWI-14, MWI-17 and MWI-18 are virtually identical to I1V, I2V and I3V, and results for them are not shown separately.

@@

\subsection{AWS}
%
%t
\begin{table*}[t]
	\caption{Same as Table~\ref{tab:error_statistics_ici}, but for channels AWS channels. Results are from QRNN-single. }
	\label{tab:statistics_qrnn_aws}
	\begin{tabular}{llrr|rrr}
		\tophline
		&&\multicolumn{2}{c|}{Simulations}& \multicolumn{3}{c}{QRNN-single} \\
		\cline{3-7}
		%		\hline
		&&   Clear-sky &   All-sky &  Filtered(5\,K) & Predicted & Predicted(5\,K) \\
		\middlehline
		AWS-32  &bias     & 0.00 & -1.32 & -0.26 & -0.03 & -0.02 \\
				&mae      & 0.36 &  1.57 &  0.52 &  0.54 &  0.43 \\
				&std      & 0.46 &  6.42 &  0.85 &  1.02 &  0.61 \\
				&skewness & 0.01 & -8.43 & -3.65 & -0.07 & -1.98 \\
		\middlehline
		AWS-33	&Bias     & -0.01 & -0.98 & -0.25 & 0.02 &  0.01 \\
				&MAE      &  0.36 &  1.23 &  0.51 & 0.49 &  0.42 \\
				&STD      &  0.45 &  4.70 &  0.80 & 0.76 &  0.56 \\
				&skewness & -0.00 & -8.78 & -2.92 & 0.04 & -0.79 \\
